Should geophysicists use gravity anomaly or gravity disturbance?

### 2018-05-11 manuscript/letter.tex
Fix author line too long using a parbox

\author[Oliveira Jr et al.]
{Vanderlei C. Oliveira Jr$^1$\thanks{Email: vanderlei@on.br},
Kristoffer A. T. Hallam$^{1}$, Val\'{e}ria C. F. Barbosa$^1$
and Leonardo Uieda$^2$ \\
$^1$ Department of Geophysics, Observat\'{o}rio Nacional, Rio de Janeiro, Brazil \\
$^2$ Department of Geology and Geophysics, SOEST, University of Hawai'i at M\={a}noa, Honolulu, USA
}

>>>>

\author[Hallam et al.]{
\parbox{\linewidth}{%
    Kristoffer A. T. Hallam$^{1}$\thanks{Emails: kristoffer.hallam@gmail.com, vanderlei@on.br},
    Vanderlei C. Oliveira Jr$^1$,
    Val\'{e}ria C. F. Barbosa$^1$, and \linebreak Leonardo Uieda$^2$
    \vspace{0.3cm}
}%
    \\
    $^1$ Department of Geophysics, Observat\'{o}rio Nacional, Rio de Janeiro, Brazil \\
    $^2$ Department of Geology and Geophysics, SOEST, University of Hawai'i at M\={a}noa, Honolulu, USA
}
